\subsection{Product Comparisons}
As stated by our initial problem; can an ordinary webcam compare to other gaming platforms? It is necessary to figure out which other gaming platforms to compare the webcam with. Since the webcam is a video camera it can be easily be compared with other video game platforms that utilize a video camera. The Xbox Kinect from Microsoft utilizes one RGB-camera and two 3D depth sensors to detect gestures made by the user \parencite{Cong}. The Kinect is popular, having sold roughly 24 million sensors during its current lifespan \parencite{MSByNumbers}, and because it has become such a household name, makes it a suitable platform for comparison.
\bigskip

Another popular brand is the Wii by Nintendo. The Wii was introduced in 2006 and was the first console to have motion control. During its lifespan the Wii has sold near 100 million units worldwide \parencite{NintendoSales}. The Wii also uses a camera but not in the same way as the Microsoft Kinect, instead of using a static VGA camera like the Kinect, the Wii uses an infrared camera positioned within the hand-held controller held by the user to detect the position of the controller in relation to the monitor \parencite{Castaneda2006}. This makes the controller usable as a pointing device. The Wii controller also uses motion sensors to detect the tilting of the controller, which allows the controller to be used as a virtual golf club or tennis racket. The Wii's use of camera technology, makes it suitable for comparison.
\bigskip

The PlayStation Move by Sony was introduced as an add-on to the PlayStation 3 in 2010. The Move uses a video camera in conjunction with motion sensors in a hand-held controller to detect the users position in the 3D space \parencite{Kumar2009}. The move works in many ways as the Nintendo Wii except for the use of camera technology, the Move controller has a visible light on the top of the controller which the camera uses to pinpoint the location of the controller. While the Move is not as popular as the two other products, having sold around 15 million units so far \parencite{Yin-Poole2012}, its use of the camera solution makes it usable for a comparison.
