\section{Analysis} \label{sec:analysis}
The purpose of this analysis is to collect the relevant research and data which was deemed necessary during the naïve design phase. This research is going to be used as a basis for a prototype, which should help us answer our problem statement. 

\input{./chapters/analysis/product_comparisons}
\input{./chapters/analysis/sota}
\input{./chapters/analysis/wheel}
\input{./chapters/analysis/controls}
\input{./chapters/analysis/visual_computing}
\input{./chapters/analysis/image_video}
\input{./chapters/analysis/gesture}
\input{./chapters/analysis/user_control}

\subsection{Analysis summary}
From the analysis, some key elements were found, in regards to the initial problem statement, and how to create a solution for the problem.

The first point that becomes apparent is that while the initial problem statement is technically solved by using Camspace, it also proves to be insufficient for the desired use, as the controls are limited to movement, and not special actions. This is further emphasized as a problem when looking at the fact, that none of the researched racing games make do with simply movement, they all have one or more additional features, which are essential for the game play.

Another important section of knowledge gained from the analysis, is the different ways to create the program. The analysis shows different methods of doing it, and gives arguments for how each method could be used, which will help deciding, when the product is going to be designed.
From the analysis, the initial problem statement can be modified, and turned into a final problem statement, on which the continuing project can be based.

\input{./chapters/analysis/fps}