\section{Conclusion}
Through the naïve design process in the beginning of the project, it was found that research areas such as image processing and gesture recognition had to be researched further in order to get a clear understanding of the initial problem.
\bigskip

The analysis of the research areas led to an understanding of how the state of the art products functioned and how they utilized image-processing techniques. 
It was found that color recognition was a viable method of detecting features in a webcam feed to detect gestures. 
An alternative method had been fiducial recognition; 
however, this would have been time consuming considering the amount of time given to this project. 
Therefore, color recognition in combination with BLOB analysis was the preferred method for the purpose of this project. 
It was found that basic functionality in a vehicle game included steering, acceleration, gear shifting, as well as some extra function often hand braking or change of camera view, these were the functions that the product had to incorporate. 
Based on our research it was possible to reach a final product statement as well as a list of requirements for a solution.
\bigskip

In order to fulfill this final problem statement a testable design was picked out of three possible solutions. 
The final design incorporates the researched areas from the analysis as well as the list of requirements. 
The design utilized color detection paired with BLOB analysis to detect the gestures of the user. 
The design utilizes multithreading to translate the gestures into input to the tested vehicle game.
\bigskip

The testing of the design showed that the design had certain flaws concerning the detection of some of the gestures, which resulted in involuntary activation of functions. 
It was concluded that the product worked with only some slowdown to the computer, the product introduced some delay to the activation of some of the functions. 
It was found that many of the test subjects had difficulty operating the controller.
\bigskip

It is not possible to accurately conclude upon the final problem statement because some of the predefined basic functionality of the controller was not operational for testing.  
The testing showed that it was possible to apply several detection mechanisms to a webcam feed without much overhead to the PC; 
we therefore see no reason why a properly implemented gear shifting mechanism would not be possible. 
