\section{List of Requirements}
\label{LOR}

\textit{The content of the list of requirements is to be seen as parameters for the product design. The arguments have been refined in the analysis-chapter, and have ultimately led to these requirements, that will help construction of the final product. Hence it is to be considered a blueprint from which numerous variations of designs can be crafted.}
\bigskip

General requirements:
\begin{itemize}
\item The controller must be for controlling vehicle games.
\item The controller must utilize visual computing within the limitations of a webcam.
\item The controller must be comparable to pre-existing controllers in terms of functionality and playability.
\end{itemize}
Hardware requirements:
\begin{itemize}
\item The solution must require a standard webcam.
\item The solution must require a computer to run the software.
\item the standard webcam does not have to be embedded in the computer. Therefore computer type is relevant.
\item No additional hardware required for the sake of control of the vehicle game.
\end{itemize}
Software requirements:
\begin{itemize}
\item The controller software must be compatible with a pre-existing vehicle game which supports the game functionalities as described in \ref{LOR} Controller functionalities. 
\item The output of the software should mimic input to conventional input methods like keyboard presses or mouse movements.
\item the controller software must track either colors, patterns or both.
\end{itemize}
Controller functionalities:
\begin{itemize}
\item Steering left and right
\item Acceleration
\item Braking and/or driving reverse
\item Gear shift
\item (Optional) action button for utilities 
\end{itemize}