\section{Naïve designs}
The usual structure of a project like this starts with developing an idea of some problem and formulate this into an initial problem statement. This is followed by doing some initial research, called investigation, with the goal of turning the idea into an final and more specific problem statement, which is then used to narrow the field of research into an analysis, with the goal of specifying a list of requirements for a design.

This report structure here is somewhat similar in content, but different in approach:
After defining the initial problem statement it is used as a framework for creating some naïve designs. These designs are then used to figure out which areas of research should be focused on, i.e. they effectively work as the investigation chapter.
\bigskip

The reason this approach is used, is to increase efficiency and broadening the perspective of possible solutions to a problem. Instead of doing a lot of preliminary research on a subject, in order to create a final problem statement, the order is reversed, which reduces the amount of work that "goes to waste" i.e. ends up not being important for the project, and instead of risking locking upon a single solution, this approach tries to focus on many possibilities to solve a problem.
\bigskip

The method used in creating the designs starts as a brain storm, revolving around ways in which the initial problem statement \textit{could} be answered. The ideas from this brain storm, will then be used to create some design concepts, explaining how a product can be created, how it is intended to work and how it is used to answer the problem. Once the designs are made, thought will go into which elements needs further research, in order to actually make the product described, and to make sure that it \textit{actually} tests, what it is supposed to.

\input{./chapters/naive_designs/naive_design_summaries}
\input{./chapters/naive_designs/Focusing_the_research_areas}