\subsection{Results} \label{sec:results}
This section covers the results which have been collected.


\subsubsection{Quantitative data}
The following quantitative data has been accounted for:

\begin{itemize}
\item \textbf{Subject no:} Specifies the number of the participant.
\item \textbf{Controller sequence:} Indicates the sequence for which the contestant played a lap with either of the controllers first and then afterwards the other.
\item \textbf{Product time:} Describes the time for which the lap has been completed with the developed product.
\item \textbf{SOTA time:} describes the time for which the lap has been completed with the Xbox controller (State of the Art controller).
\end{itemize}

\input{./appendices/timemeasurements_table}


\subsubsection{Qualitative data}
The qualitative data covers the observations of the gameplay from each of the test subjects. 
Also, the qualitative data covers recorded interviews of each test subject right after a lap with either of the controllers, which has been converted into text.


\subsubsection{Interview}
Full interview notes: appendix \ref{app:interview}.

After each lap with any of the controllers, the test subject is asked to answer questions, which concerns the following question templates.

\begin{enumerate}
\item Did you experience any Function delay that affected the gameplay?
\item Did you experience any Non responsiveness of functions that affected the gameplay?
\item Did you experience any difficulty activating game functions that affected the gameplay?
\item Did you experience any complications with enabling consecutive game functions (using functions together in context) that affected the gameplay? 
\item Did you experience any complications with the controller movement and handling that affected the gameplay?
\end{enumerate}

The answers which were obtained from the test subjects were recorded. 
Thereafter the answers from the test subjects are combined and placed below the identified relevant question.